Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2020-08-20 papers/paper/paper.tex
Add section on how we fit parameters to paper.tex

  \section*{Calculating leading/lagging probability vs displacement}

  \section*{Calculating force-dependent velocities}

>>>>

  %% \section*{Calculating leading/lagging probability vs displacement}

  %% \section*{Calculating force-dependent velocities}

\section*{Fitting model parameters}

\subsection*{$L_t$, $L_s$, $R_b$, $R_m$, $R_s$, $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$}
Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}. In the class average image from Burgess \textit{et. al.} \cite{burgess} the different tail-motor-MTBD angles were taken to indicate that left stalk's motor domain was in the apo post-powerstroke state, and the right stalk's motor domain in the ADP-bound pre-powerstroke state. In the Grotjahn \textit{et. al} \cite{grotjahn} density map, both motor domains were taken to be in the post-powerstroke state.

\subsection*{$c_b$, $c_m$, $c_t$}
Spring constants $c_b$, $c_m$ and $c_t$ were fit using the dynein step length distribution from \cite{yildizpaper}. Three spring constants were drawn uniformly from range $[0.0, 4.0]$ and a simulation was run for 10s simulation time with $k_b=X$, $k_{ub}=Y$, $k_{stk}=Z$, and other parameters noted in Table \ref{tab:params}. One thousand simulations total were run, and the set of spring constants which yielded the lowest root-mean-squared histogram error between the simulation and experimental step length distributions was chosen. \textbf{Probably need to rerun this using our final $k_b$, $k_{ub}$ and $k_{stk}$.}

\subsection*{$k_{ub}$}
The unbinding rate $k_{ub}$ was estimated from velocity data in the Yildiz \textit{et. al.} experiment. The $k_{ub}$ value which led to an average velocity of 124 nm/s was chosen, as shown in Figure \ref{fig:behavior}.

\subsection*{$c$}
The exponential unbinding parameter $c$ was estimated using the likelihood of leading/lagging head unbinding vs interhead separation data provided in DeWitt \textit{et. al.} \cite{dewitt}. The value of $c$ was chosen which led to the lowest root-mean-squared error in P(lagging step) vs interhead separation between the experiment and the model, as shown in Figure \ref{fig:tensiongating}. All other parameters were held at the values in Table \ref{tab:params}.

\subsection*{$k_b$, $k_{stk}$}
The sticky rate and binding rate were chosen ... based on the Yildiz initial-vs-final displacement slope?
